Robust Spectroscopic Inference with Imperfect Models

### 2014-11-03 tex/paper.tex
full editing by SA (last time!)

%\documentclass[preprint]{aastex} 
\documentclass[iop,floatfix,twocolappendix]{emulateapj}

@@

In this article, we design a flexible forward-modeling approach to the general spectroscopic 
inference problem in a Bayesian framework, building on the best aspects of the latter two methods 
highlighted above.  Employing a non-trivial covariance matrix parameterized by both global 
(stationary) and local (non-stationary) Gaussian process kernels, we are able to account for 
residual pixel-to-pixel correlations that arise when comparing observed spectra to intrinsically 
imperfect models.  This approach minimizes the potential for bias, efficiently propagates 
systematic uncertainties into the parameter inferences, and ultimately can serve as tool for using
observations to guide substantial improvements in the models themselves.  An overview of the 
methodology of this approach is provided in Section \ref{sec:method}, including the covariance 
matrix formalism.  Some tests and example applications (for a high resolution optical spectrum of 
an F star, and a medium-resolution near-infrared spectrum of a mid-M star) of the method are 
described in Section \ref{sec:examples}.  Finally, a discussion of the potential utility of the 
technique, and the possibility of extending it to develop data-driven spectral models, is provided 
in Section \ref{sec:discussion}.  \\

@@

The remainder of this Section describes the mechanics of this modeling framework.  First, a model 
spectrum is generated for a given set of physical parameters (Section \ref{subsec:synthetic}), and 
then post-processed to mimic reality using a set of observational and practical nuisance parameters 
(Section \ref{subsec:postprocess}).  Next, a direct, pixel-by-pixel comparison between the data and 
model spectra is made with a prescribed likelihood function and a parametric treatment of the 
covariances between pixel residuals (Section \ref{subsec:likelihood}).  That process is iterated 
under the guise of hierarchical Markov Chain Monte Carlo (MCMC) simulations to numerically explore 
the posterior probability density of the model conditioned on the data, and thereby to determine 
constraints on the parameters of interest (Section \ref{subsec:MCMC}).  Along the way, these 
procedures are illustrated with real observations of the high resolution optical spectrum from a 
nearby F star.  That specific application, along with some alternative demonstrations of the 
method, are discussed in more detail in Section \ref{sec:examples}.

@@

We opt for the computationally expedient approach that employs a library of model spectra, 
$\flam(\{\vt_{\ast}\}^{\rm grid})$, where $\vt_{\ast} = [T_{\rm eff}, \,\, \log{g}, \,\, 
[{\rm Fe/H}]]$.  However, it is worth noting that the techniques developed here are applicable to 
{\it any} ``back-end" that generates a model spectrum.  In our adopted approach, the model spectrum 
for an arbitrary $\vt_{\ast}$ is interpolated from a spectral library,
\begin{equation} \label{eqn:interp} 
\flam(\{\vt_{\ast}\}^{\rm grid}) \leadsto \flam(\vt_{\ast}), 
\end{equation} 
where we assign the symbol $\leadsto$ as an interpolation operator.  The multi-dimensional 
interpolation in Eq.~\ref{eqn:interp} needs to be performed many times, so computational efficiency 
is critical.  In practice, a simple tri-linear interpolation is suitably fast, but introduces a 
non-negligible level of uncertainty.  These interpolation uncertainties can be empirically 
estimated by performing the operation in Eq.~\ref{eqn:interp} across a $\{\vt_{\ast}\}^{\rm grid}$ 
grid point, and then comparing the interpolated spectrum with the corresponding library spectrum 
\citep[see also][]{husser12}.  We have developed this approach to propagate the interpolation 
uncertainties into the likelihood calculations, as described briefly in 
Section~\ref{subsec:likelihood} and elaborated in the Appendix.

@@

We can further divide $\vt_{\rm obs}$ into those parameters that impact the model primarily in the 
spectral or flux dimensions.  For the former, we consider three kernels that contribute to the 
line-of-sight velocity distribution function, $\varphi_v$.  The first, $\mathcal{F}_v^{\rm inst}$, 
treats the instrumental spectral broadening.\footnote{For computational efficiency, we first 
pre-convolve the entire raw spectral library with a slight under-prediction of $\mathcal{F}_v^{\rm 
inst}$ and resample the spectra to a lower resolution.  Because the instrumental point spread 
function acts as a low-pass filter, this procedure reduces the size of the library by a factor of 
10 or more while still preserving the final Fourier content of the spectra.  Then, when any given 
spectrum is post-processed, the actual $\mathcal{F}_v^{\rm inst}$ used is treated as a smaller 
``correction" to this pre-processing kernel.}  For illustrative purposes, we assume 
$\mathcal{F}_v^{\rm inst}$ is a Gaussian with mean $v = 0$ and constant width $\sigma_v$ at all 
$\lambda$, although more sophisticated forms could be adopted.  The second, $\mathcal{F}_v^{\rm 
rot}$, characterizes the broadening induced by (projected) stellar rotation, parameterized by 
$v\sin{i}$ as described by \citet[][his Eq.~18.14]{gray08}.  And the third, $\mathcal{F}_v^{\rm 
dop} = \delta(v-v_z)$, incorporates the radial velocity through a Doppler shift.  The model 
spectrum is modified by the parameters $[\sigma_v, \,\, v\sin{i}, \,\, v_z]$ through these kernels, 
using a convolution in velocity-space,\footnote{In practice, these convolutions are performed as 
multiplications in Fourier-space to better preserve spectral information \citep[cf.,][]{tonry79}; 
the mathematical formalism is presented for clarity.}
\begin{eqnarray} \label{eqn:broadening}
\flam(\vt_{\ast}, \sigma_v, v\sin{i}, v_z) &=& \flam(\vt_{\ast}) \otimes \varphi_v \\
                                           &=& \flam(\vt_{\ast}) \otimes \mathcal{F}_v^{\rm inst} \otimes \mathcal{F}_v^{\rm rot} \otimes \mathcal{F}_v^{\rm dop}, \nonumber
\end{eqnarray} 
and then re-sampled onto the discrete wavelengths corresponding to each data pixel, 
\begin{equation} \label{eqn:resampling}
\flam(\vt_{\ast},  \sigma_v, v\sin{i}, v_z) \mapsto \vM(\vt_{\ast},  \sigma_v, v\sin{i}, v_z),
\end{equation}
where the $\mapsto$ symbol denotes a re-sampling operator that maps the model spectrum onto the 
$N_{\rm pix}$-element model vector $\vM$ ($N_{\rm pix}$ is the number of pixels in the spectrum).  
Figure \ref{fig:broadening} shows a (condensed) graphical representation of these post-processing 
steps.

@@

We employ an analogous, but more rigorous, approach to deal with this issue, cast {\it internal} to 
the modeling framework to propagate the uncertainties introduced by additional degrees of freedom 
in the model.  Deviations in the spectral shape introduced by calibration residuals are treated as 
explicit contributions to the model spectrum, enabling an exploration of the distribution of 
possible ``tweaks" to the calibration that can be compartmentalized into a set of nuisance 
parameters and then marginalized.  This way, the inferences for the stellar parameters will 
properly account for the underlying uncertainty in the calibration of the spectral shape.  In 
practice, this is achieved by distorting segments of the model spectrum with polynomials, 
$\mathsf{P}$ \citep[e.g.,][]{eisenstein06,koleva09}.  For data that has $N_{\rm ord}$ spectral 
orders, each denoted with index $o$, the model spectrum can be decomposed into the set of orders
\begin{eqnarray} \label{eqn:chebyshev}
\vM(\vT, \cheb) &=& \{ \vM_o(\vT) \times \mathsf{P}_o \} \\
                &=& \{ \vM_o(\vT) \times \sum_n c_o^{(n)} \, T_o^{(n)} \}, \nonumber
\end{eqnarray}
where $T^{(n)}$ is the $n^{\rm th}$ degree Chebyshev function.  The $n \times N_{\rm ord}$ 
coefficients are considered a set of nuisance (hyper-)parameters, $\cheb = [\{c_o^{(0)}, c_o^{(1)}, 
\ldots, c_o^{(n-1)} \}]$.  With judicious priors, we can ensure that the unintended treatment of 
real spectral features (e.g., molecular bands) as residual calibration artifacts is negligible.  
The lowest-degree (scaling) coefficient, $c^{(0)}$, is naturally degenerate with the solid angle, 
$\Omega$.  Therefore, we enforce an additional constraint that the mean of the polynomial is 
unity.  For data with a single spectral order, this means simply setting $c^{(0)} = 1$.  In the 
multiple order case, we assign $c^{(0)} = 1$ in an arbitrary order as an anchor, but permit the 
$c^{(0)}$ in other orders to be different.  Figure \ref{fig:chebyshev} offers a practical 
demonstration of how these nuisance parameters are applied to the model.

@@

For a well-designed spectrograph and sufficiently accurate model, this {\it global} (i.e., present 
throughout the spectrum) covariant structure should have a relatively low amplitude and small 
correlation length.  To describe that structure, we use a stationary covariance kernel (or radial 
basis function) with an amplitude that depends only on the velocity distance between two pixels, 
\begin{equation}
  r_{ij} = r(\lambda_i, \lambda_j) = \Delta v = \frac{c}{2} \left | \frac{\lambda_i 
   - \lambda_j}{ \lambda_i + \lambda_j} \right |,
\end{equation}
where $c$ is the speed of light.  This parametric kernel describes the covariance between pixel 
residuals, 
\begin{equation}
  \Kglobal_{ij} =  \langle \vR_i \; \vR_j \rangle.
  \label{eqn:expectation}
\end{equation}
A variety of kernels have been used in the field of Gaussian processes to parameterize such a 
covariant structure \citep[e.g.,][]{rasmussen05}.  Here, we adopt the commonly-employed \matern\ 
kernel with $\nu = 3/2$,
\begin{equation}
  \Kglobal_{ij}(\vp_{{\mathsf C}, g}) = a_{\rm g} \left(1 + \frac{\sqrt{3}\, r_{ij}}{\ell} \right ) \exp 
   \left (- \frac{\sqrt{3}\, r_{ij}}{\ell} \right ),
   \label{eqn:global}
\end{equation}
where the (hyper-)parameters $\vp_{{\mathsf C}, g} = [a_g, \ell]$ include an amplitude ($a_g$) and 
scale ($\ell$).  To ensure that $\vC$ remains a relatively sparse matrix that 
enables computational expendiency, we employ a Hann window function
\begin{equation}
  w_{ij}^{\rm g} \,(r_0) = \left \{ 
    \begin{array}{cc}
    \frac{1}{2} + \frac{1}{2} \cos \left(\frac{\pi r_{ij}}{r_0} \right) & r_{ij} \le r_0 \\
    0 & r_{ij} > r_0 \\
  \end{array}
  \right .
  \label{eqn:Hann}
\end{equation}
as a taper.  The truncation distance $r_0$ can be fixed to a reasonable multiple of the 
scale (we set $r_0 = 4\ell$).

@@

The procedure outlined above can be a significant computational challenge.  A
typical data spectrum has $N_{\rm pix} > \mathcal{O}(10^3)$, and therefore the
many repeated evaluations of the matrix product $\vR^{\trans} \vC^{-1} \vR$ in
the likelihood calculation can be numerically expensive.  However, because
$\vC$ is a symmetric, positive semi-definite matrix, we can employ Cholesky
factorization to optimize the evaluation of the matrix product ($\vR^{\trans}
\vC^{-1} \vR$) and avoid the direct calculation of the matrix inverse
($\vC^{-1}$) itself.  For echelle spectra with multiple orders or multiple
spectra of the same object, taken with different instruments, the nuisance
parameters for each chunk of spectrum are independent from the other chunks. This
means that the computationally intensive steps of generating a model spectrum
for a specific wavelength range and evaluating the likelihood can be
parallelized. The only segment of the code that needs to be synchronized is the
MCMC proposal of stellar parameters, which are shared between all chunks of the
spectrum. Because all of the computationally expensive steps can be
parallelized, this algorithm can be massively parallelized on a cluster,
enabling simultaneous inference for wide spectral ranges at high resolution or
multiple spectral datasets acquired with different instruments. To sample this
model, we extend the Metropolis-Hastings sampler included in the {\tt emcee}
package \citep{foreman-mackey13} to function within a parallelized blocked
Gibbs sampler.\footnote{\url{https://github.com/iancze/emcee}}\\

@@

Given the decision to employ a spectral library to generate models (Sect.~\ref{subsec:synthetic}), 
a direct comparison of the \citeauthor{torres12}~{\tt SPC} result with our framework is most 
relevant.  Using the same TRES spectral orders, the {\sc CfA/Kurucz} library, and a 
$\delta$-function prior on $\log g$ (at 4.29), we infer parameters that are consistent with the 
{\tt SPC} approach; see Table~\ref{table:Kurucz}.  Figure~\ref{fig:Kurucz_residuals} demonstrates 
the quality of our approach in reproducing the WASP-14 spectrum and, especially significant, the 
structure of the residuals.  Figure~\ref{fig:Kurucz_posterior} shows some marginal projections of 
the posterior-space, highlighting key parameter degeneracies.

@@

\capstartfalse
\begin{deluxetable}{lr@{ $\pm$ }l|r@{ $\pm$ }l}[!b]
\tablecaption{\label{table:Kurucz}Inferred Parameters for WASP-14}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{{\sc CfA/Kurucz}} & \multicolumn{2}{c}{{\sc Phoenix}}}
\startdata
$T_{\rm eff}$ (K) & 6424     & 19                      &  6354   & 39        \\
$\log g$      & 4.29     & 0 (fixed)               &  4.29   & 0 (fixed) \\
$\Z$          & -0.26    & 0.01                    & -0.30  & 0.02     \\
$v \sin i$ ($\kms$)\tablenotemark{a}   & 4.47 & 0.06       &  5.09   & 0.06      \\
$v_z$ ($\kms$)        & -4.60    & 0.02                    & -4.86   & 0.02      \\
$\log \Omega$\tablenotemark{b} & -12.7180 & 0.0004 & -12.717 & 0.0007 \\
$A_V$                          & 0        & 0 (fixed) & 0 & 0 (fixed)
\enddata
\tablenotetext{a}{Small differences in the rotational broadening between the two libraries are
expected, since they assume different micro- and macro-turbulence behavior in the stellar
atmospheres.}
\tablenotetext{b}{For the spectral emulator (Appendix~\ref{sec:Appendix}) the spectra are scaled such that the average flux is unity, rather than given in units of flux at the stellar surface, so this value is an unknown multiple of $R^2/d^2$.}
\tablecomments{The quoted values represent the ``best-fit", the peak of the marginal posterior 
distributions for each parameter.  The quoted uncertainties correspond to the 68.3\%\ 
($\sim$1\,$\sigma$) confidence intervals.  Expanded lists of the inferred values and uncertainties 
for all nuisance parameters are available electronically.}
\end{deluxetable}
\capstarttrue

@@

It is worthwhile to comment on the inferred parameter uncertainties.  In this specific example, 
some experimentation with restricted forms of the covariance matrix confirm that the uncertainties 
of the interesting parameters have roughly equal contributions from trivial (Poisson) noise, grid 
interpolation errors, and a non-trivial global covariance term.\footnote{Note that the {\sc 
CfA/Kurucz} library has been specifically well-tuned for stars like WASP-14, by careful variation 
of atomic data (e.g., line lists, oscillator strengths) with reference to observations of the Sun 
and Vega, by J.~Morse and J.~B.~Laird.  Over this limited spectral range, this means that no local 
covariance kernels need to be instantiated to reproduce the residual structure.}  For synthetic 
models that are less well-tuned than the {\sc CfA/Kurucz} grid, the latter two terms will certainly 
dominate.  In any case, these uncertainties are still considerably smaller than the ``floor" values 
imposed by \citet{torres12}, but they are representative of our expectations for comparing data of 
high sensitivity and volume with models of limited parametric flexibility (i.e., the uncertainties 
would inflate considerably if the many fixed or restricted parameters that went into building the 
model libraries were available for variation).

@@

Aside from the structure of the covariance matrix, there is also a moderate difference between the 
posterior distributions of the stellar parameters inferred using the {\sc Phoenix} and {\sc 
CfA/Kurucz} libraries: see Table~\ref{table:Kurucz} and compare Figures~\ref{fig:Kurucz_posterior} 
and \ref{fig:PHOENIX_posterior}.  The {\sc Phoenix} models find a systematically cooler temperature 
(by $\sim$75\,K) and lower metallicity than inferred from the {\sc 
CfA/Kurucz} models.  Because our framework explicitly mitigates the potential for posterior bias 
from imperfect matches between data and models, we can safely conclude that these apparent 
discrepancies are intrinsic to the different input physics of the model libraries.\footnote{It is 
worth noting that these differences are not a manifestation of the stringent prior on surface 
gravity.  When the spectra are modeled with $\log g$ unconstrained, the posteriors for both 
libraries shift, but their respective discrepancies actually increase slightly.}  Such a comparison 
serves as a stark reminder that incomplete and/or over-simplified physical prescriptions remain the 
most significant source of systematic uncertainty in estimates of fundamental stellar parameters.

@@

As a point of reference, \citet{rojas-ayala12} used a $K$-band spectrum at similar resolution to 
the SPEX data to estimate the basic Gl~51 parameters using an index technique.  They measured 
equivalent widths for the 2.205\,$\mu$m \ion{Na}{1} doublet and 2.263\,$\mu$m \ion{Ca}{1} triplet, 
along with a pseudo-continuum index defined over three narrow passbands, 2.070--2.090, 
2.235--2.255, and 2.360--2.380\,$\mu$m (see their Fig.~2 for a useful visualization), designed to 
probe the spectral curvature induced by H$_2$O absorption bands.  With reference to a custom grid 
of the {\sc BT-Settl} modifications of the {\sc Phoenix} library \citep{allard12}, 
\citeauthor{rojas-ayala12}~infer $T_{\rm eff} = 3039\pm56$\,K and $[{\rm Fe/H}] = 0.28\pm0.17$ for 
a fixed $\log g = 5.0$.

@@

\section{Spectral Emulator} \label{sec:Appendix}

>>>>

%\documentclass[preprint]{aastex} 
\documentclass[iop,floatfix,numberedappendix,twocolappendix]{emulateapj}

@@

In this article, we design a flexible forward-modeling approach to the general spectroscopic 
inference problem in a Bayesian framework, building on the best aspects of the latter two methods 
highlighted above.  Employing a non-trivial covariance matrix parameterized by both global 
(stationary) and local (non-stationary) Gaussian process kernels, we are able to account for 
residual pixel-to-pixel correlations that arise when comparing observed spectra to intrinsically 
imperfect models.  This approach minimizes the potential for bias, efficiently propagates 
systematic uncertainties into the parameter inferences, and ultimately can serve as a tool for 
using observations to guide substantial improvements in the models themselves.  An overview of the 
methodology of this approach is provided in Section \ref{sec:method}, including the covariance 
matrix formalism.  Some tests and example applications (for a high resolution optical spectrum of 
an F star, and a medium-resolution near-infrared spectrum of a mid-M star) of the method are 
described in Section \ref{sec:examples}.  Finally, a discussion of the potential utility of the 
technique, and the possibility of extending it to develop data-driven spectral models, is provided 
in Section \ref{sec:discussion}.  \\

@@

The remainder of this Section describes the mechanics of this modeling framework.  First, a model 
spectrum is generated for a given set of physical parameters (Section \ref{subsec:synthetic}; 
Appendix~\ref{sec:Appendix}), and then post-processed to mimic reality using a set of observational 
and practical nuisance parameters (Section \ref{subsec:postprocess}).  Next, a direct, 
pixel-by-pixel comparison between the data and model spectra is made with a prescribed likelihood 
function and a parametric treatment of the covariances between pixel residuals (Section 
\ref{subsec:likelihood}).  That process is iterated under the guise of hierarchical Markov Chain 
Monte Carlo (MCMC) simulations to numerically explore the posterior probability density of the 
model conditioned on the data, and thereby to determine constraints on the parameters of interest 
(Section \ref{subsec:MCMC}).  Along the way, these procedures are illustrated with observations of 
the high resolution optical spectrum from a nearby F star.  That specific application, along with 
some alternative demonstrations of the method, are discussed in more detail in Section 
\ref{sec:examples}.

@@

We opt for the computationally expedient approach that employs a library of model spectra, 
$\flam(\{\vt_{\ast}\}^{\rm grid})$, where $\vt_{\ast} = [T_{\rm eff}, \,\, \log{g}, \,\, 
[{\rm Fe/H}]]$.  However, it is worth noting that the techniques developed here are applicable to 
{\it any} ``back-end" that generates a model spectrum.  In our adopted approach, the model spectrum 
for an arbitrary $\vt_{\ast}$ is interpolated from a spectral library,
\begin{equation} \label{eqn:interp} 
\flam(\{\vt_{\ast}\}^{\rm grid}) \leadsto \flam(\vt_{\ast}), 
\end{equation} 
where we assign the symbol $\leadsto$ as an interpolation operator.  The multi-dimensional 
interpolation in Eq.~\ref{eqn:interp} needs to be performed many times, so computational efficiency 
is critical.  In practice, a simple tri-linear interpolation is suitably fast, but introduces a 
non-negligible level of uncertainty.  These interpolation uncertainties can be empirically 
estimated by performing the operation in Eq.~\ref{eqn:interp} across a $\{\vt_{\ast}\}^{\rm grid}$ 
grid point, and then comparing the interpolated spectrum with the corresponding library spectrum 
\citep[see also][]{husser12}.  To suitably propagate the interpolation uncertainties into the 
likelihood calculations, we employ a Bayesian emulation technique that is described in detail in 
Appendix \ref{sec:Appendix}.

@@

We can further divide $\vt_{\rm obs}$ into those parameters that impact the model primarily in the 
spectral or flux dimensions.  For the former, we consider three kernels that contribute to the 
line-of-sight velocity distribution function, $\varphi_v$.  The first, $\mathcal{F}_v^{\rm inst}$, 
treats the instrumental spectral broadening.\footnote{For computational efficiency, we first 
pre-convolve the entire raw spectral library with a slight under-prediction of $\mathcal{F}_v^{\rm 
inst}$ and resample the spectra to a lower resolution.  Because the instrumental point spread 
function acts as a low-pass filter, this procedure reduces the size of the library by a factor of 
10 or more while still preserving the final Fourier content of the spectra.  Then, when any given 
spectrum is post-processed, the actual $\mathcal{F}_v^{\rm inst}$ used is treated as a smaller 
``correction" to this pre-processing kernel.}  For illustrative purposes, we assume 
$\mathcal{F}_v^{\rm inst}$ is a Gaussian with mean $v = 0$ and constant width $\sigma_v$ at all 
$\lambda$, although more sophisticated forms could be adopted.  The second, $\mathcal{F}_v^{\rm 
rot}$, characterizes the broadening induced by (projected) stellar rotation, parameterized by 
$v\sin{i}$ as described by \citet[][his Eq.~18.14]{gray08}.  And the third, $\mathcal{F}_v^{\rm 
dop} = \delta(v-v_z)$, incorporates the radial velocity through a Doppler shift.  The model 
spectrum is modified by the parameters $[\sigma_v, \,\, v\sin{i}, \,\, v_z]$ through these kernels, 
using a convolution in velocity-space,\footnote{In practice, these convolutions are performed as 
multiplications in Fourier-space to better preserve spectral information \citep[cf.,][]{tonry79}; 
the mathematical formalism is presented for clarity.}
\begin{eqnarray} \label{eqn:broadening}
\flam(\vt_{\ast}, \sigma_v, v\sin{i}, v_z) &=& \flam(\vt_{\ast}) \ast \varphi_v \\
                                           &=& \flam(\vt_{\ast}) \ast \mathcal{F}_v^{\rm inst} \ast \mathcal{F}_v^{\rm rot} \ast \mathcal{F}_v^{\rm dop}, \nonumber
\end{eqnarray} 
and then re-sampled onto the discrete wavelengths corresponding to each data pixel, 
\begin{equation} \label{eqn:resampling}
\flam(\vt_{\ast},  \sigma_v, v\sin{i}, v_z) \mapsto \vM(\vt_{\ast},  \sigma_v, v\sin{i}, v_z),
\end{equation}
where the $\mapsto$ symbol denotes a re-sampling operator that maps the model spectrum onto the 
$N_{\rm pix}$-element model vector $\vM$ ($N_{\rm pix}$ is the number of pixels in the spectrum).  
Figure \ref{fig:broadening} shows a (condensed) graphical representation of these post-processing 
steps.

@@

We employ an analogous, but more rigorous, approach to deal with this issue, cast {\it internal} to 
the modeling framework to propagate the uncertainties introduced by additional degrees of freedom 
in the model.  Deviations in the spectral shape introduced by calibration residuals are treated as 
explicit contributions to the model spectrum, enabling an exploration of the distribution of 
possible ``tweaks" to the calibration that can be compartmentalized into a set of nuisance 
parameters and then marginalized.  This way, the inferences for the stellar parameters will 
properly account for the underlying uncertainty in the calibration of the spectral shape.  In 
practice, this is achieved by distorting segments of the model spectrum with polynomials, 
$\mathsf{P}$ \citep[e.g.,][]{eisenstein06,koleva09}.  For data that has $N_{\rm ord}$ spectral 
orders, each denoted with index $o$, the model spectrum can be decomposed into the set of orders
\begin{eqnarray} \label{eqn:chebyshev}
\vM(\vT, \cheb) &=& \{ \vM_o(\vT) \times \mathsf{P}_o \} \\
                &=& \{ \vM_o(\vT) \times \sum_n c_o^{(n)} \, T_o^{(n)} \}, \nonumber
\end{eqnarray}
where $T^{(n)}$ is an $n^{\rm th}$ degree Chebyshev function.  The $n \times N_{\rm ord}$ 
coefficients are considered a set of nuisance (hyper-)parameters, $\cheb = [\{c_o^{(0)}, c_o^{(1)}, 
\ldots, c_o^{(n-1)} \}]$.  With judicious priors, we can ensure that the unintended treatment of 
real spectral features (e.g., molecular bands) as residual calibration artifacts is negligible.  
The lowest-degree (scaling) coefficient, $c^{(0)}$, is naturally degenerate with the solid angle, 
$\Omega$.  Therefore, we enforce an additional constraint that the mean of the polynomial is 
unity.  For data with a single spectral order, this means simply setting $c^{(0)} = 1$.  In the 
multiple order case, we assign $c^{(0)} = 1$ in an arbitrary order as an anchor, but permit the 
$c^{(0)}$ in other orders to be different.  Figure \ref{fig:chebyshev} offers a practical 
demonstration of how these nuisance parameters are applied to the model.

@@

For a well-designed spectrograph and sufficiently accurate model, this {\it global} (i.e., present 
throughout the spectrum) covariant structure should have a relatively low amplitude and small 
correlation length.  To describe that structure, we use a stationary covariance kernel (or radial 
basis function) with an amplitude that depends only on the velocity distance between two pixels, 
\begin{equation}
  r_{ij} = r(\lambda_i, \lambda_j) = \Delta v = \frac{c}{2} \left | \frac{\lambda_i 
   - \lambda_j}{ \lambda_i + \lambda_j} \right |,
\end{equation}
where $c$ is the speed of light.  This parametric kernel describes the covariance between pixel 
residuals, 
\begin{equation}
  \Kglobal_{ij} =  \langle \vR_i \; \vR_j \rangle.
  \label{eqn:expectation}
\end{equation}
A variety of kernels have been used in the field of Gaussian processes to parameterize such a 
covariant structure \citep[e.g.,][]{rasmussen05}.  Here, we adopt the commonly-employed \matern\ 
kernel with $\nu = 3/2$,
\begin{equation}
  \Kglobal_{ij}(\vp_{{\mathsf C}, {\rm g}}) = a_{\rm g} \left(1 + \frac{\sqrt{3}\, r_{ij}}{\ell} \right ) \exp 
   \left (- \frac{\sqrt{3}\, r_{ij}}{\ell} \right ),
   \label{eqn:global}
\end{equation}
where the (hyper-)parameters $\vp_{{\mathsf C}, {\rm g}} = [a_{\rm g}, \ell]$ include an amplitude 
($a_{\rm g}$) and scale ($\ell$).  To ensure that $\vC$ remains a relatively sparse matrix that 
enables computational expendiency, we employ a Hann window function
\begin{equation}
  w_{ij}^{\rm g} \,(r_0) = \left \{ 
    \begin{array}{cc}
    \frac{1}{2} + \frac{1}{2} \cos \left(\frac{\pi r_{ij}}{r_0} \right) & r_{ij} \le r_0 \\
    0 & r_{ij} > r_0 \\
  \end{array}
  \right .
  \label{eqn:Hann}
\end{equation}
as a taper.  The truncation distance $r_0$ can be fixed to a reasonable multiple of the scale (we 
set $r_0 = 4\ell$).

@@

This procedure can be a significant computational challenge.  A typical data spectrum has $N_{\rm 
pix} > \mathcal{O}(10^3)$, and therefore the many evaluations of the matrix product $\vR^{\trans} 
\vC^{-1} \vR$ in the likelihood calculation can be numerically expensive.  However, because $\vC$ 
is a symmetric, positive semi-definite matrix, we can employ Cholesky factorization to optimize the 
evaluation of the matrix product and avoid the direct calculation of the matrix inversion 
($\vC^{-1}$).  For multi-order echelle spectra or multiple spectra of the same target (perhaps 
taken with different instruments), the nuisance parameters for each segment of the spectrum are 
independent. This means that the computationally intensive steps of generating a model spectrum
for a specific wavelength range and evaluating the likelihood can be parallelized. The only segment 
of the code that needs to be synchronized is the MCMC proposal of stellar parameters, which are 
shared between all chunks of the spectrum.  The massive parallelization of this algorithm on a 
computer cluster therefore enables the simultaneous inference of interesting parameters over wide 
spectral ranges at high resolution, or from multiple datasets.  To sample the posteriors in this 
mode, we extend the Metropolis-Hastings sampler included in the {\tt emcee} package 
\citep{foreman-mackey13} to function within a parallelized blocked Gibbs 
sampler.\footnote{See \url{https://github.com/iancze/emcee}.}\\

@@

Given the decision to employ a spectral library to generate models (Sect.~\ref{subsec:synthetic}), 
a direct comparison of the \citeauthor{torres12}~{\tt SPC} result with our framework is most 
relevant.  Using the same TRES spectral orders, the {\sc CfA/Kurucz} library, and a 
$\delta$-function prior on $\log g$ (at 4.29), we infer parameters that are roughly consistent with 
the {\tt SPC} approach; see Table~\ref{table:Kurucz}.  Figure~\ref{fig:Kurucz_residuals} 
demonstrates the quality of our approach in reproducing the WASP-14 spectrum and, especially 
significant, the structure of the residuals.  Figure~\ref{fig:Kurucz_posterior} shows marginal 
projections of the posterior-space, highlighting key parameter degeneracies.

@@

\capstartfalse
\begin{deluxetable}{lr@{ $\pm$ }l|r@{ $\pm$ }l}[!b]
\tablecaption{\label{table:Kurucz}Inferred Parameters for WASP-14}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{{\sc CfA/Kurucz}} & \multicolumn{2}{c}{{\sc Phoenix}}}
\startdata
$T_{\rm eff}$ (K) & 6424     & 19                      &  6354   & 39        \\
$\log g$      & 4.29     & 0 (fixed)               &  4.29   & 0 (fixed) \\
$\Z$          & -0.26    & 0.01                    & -0.30  & 0.02     \\
$v \sin i$ ($\kms$)\tablenotemark{a}   & 4.47 & 0.06       &  5.09   & 0.06      \\
$v_z$ ($\kms$)        & -4.60    & 0.02                    & -4.86   & 0.02      \\
$\log \Omega$\tablenotemark{b} & -12.7180 & 0.0004 & -12.717 & 0.0007 \\
$A_V$                          & 0        & 0 (fixed) & 0 & 0 (fixed)
\enddata
\tablenotetext{a}{Small differences in the rotational broadening between the two libraries are
expected, since they assume different micro- and macro-turbulence behavior in the stellar
atmospheres.}
\tablenotetext{b}{For the spectral emulator (Appendix~\ref{sec:Appendix}), the models are scaled to 
an average flux of unity, rather than flux at the stellar surface; the quoted values are unknown 
multiples of $R^2/d^2$.}
\tablecomments{The quoted values represent the ``best-fit", the peak of the marginal posterior 
distributions for each parameter.  The quoted uncertainties correspond to the 68.3\%\ 
($\sim$1\,$\sigma$) confidence intervals.  Expanded lists of the inferred values and uncertainties 
for all nuisance parameters are available electronically.}
\end{deluxetable}
\capstarttrue

@@

It is worthwhile to comment on the inferred parameter uncertainties.  In this specific example, 
some experimentation with restricted forms of the covariance matrix confirms that the uncertainties 
of the interesting parameters have roughly equal contributions from trivial (Poisson) noise, grid 
interpolation errors, and a non-trivial global covariance term.\footnote{Note that the {\sc 
CfA/Kurucz} library has been specifically well-tuned for stars like WASP-14, by careful variation 
of atomic data (e.g., line lists, oscillator strengths) with reference to observations of the Sun 
and Vega, by J.~Morse and J.~B.~Laird.  Over this limited spectral range, this means that no local 
covariance kernels need to be instantiated to reproduce the residual structure.}  For synthetic 
models that are less well-tuned than the {\sc CfA/Kurucz} grid, the latter two terms will certainly 
dominate.  In any case, these uncertainties are still considerably smaller than the ``floor" values 
imposed by \citet{torres12}, but they are representative of our expectations for comparing data of 
high sensitivity and volume with models of limited parametric flexibility (i.e., the uncertainties 
would inflate considerably if the many fixed or restricted parameters that went into building the 
model libraries were available for variation).

@@

Aside from the structure of the covariance matrix, there is also a modest difference between the 
posterior distributions of the stellar parameters inferred using the {\sc Phoenix} and {\sc 
CfA/Kurucz} libraries: see Table~\ref{table:Kurucz} and compare Figures~\ref{fig:Kurucz_posterior} 
and \ref{fig:PHOENIX_posterior}.  The {\sc Phoenix} models find a systematically cooler temperature 
(by $\sim$75\,K) and lower metallicity than the {\sc CfA/Kurucz} models.  Because our framework 
explicitly mitigates the potential for posterior bias from imperfect matches between data and 
models, these apparent discrepancies must be intrinsic to the different input physics of the model 
libraries.\footnote{It is worth noting that these differences are not a manifestation of the 
stringent prior on surface gravity.  When the spectra are modeled with $\log g$ unconstrained, the 
posteriors for both libraries shift, but their respective discrepancies actually increase 
slightly.}  Such a comparison serves as a stark reminder that incomplete and/or over-simplified 
physical prescriptions remain the most significant source of systematic uncertainty in estimates of 
fundamental stellar parameters.

@@

As a point of reference, \citet{rojas-ayala12} used a $K$-band spectrum at similar resolution to 
the SPEX data to estimate the basic Gl~51 parameters using an indexing technique.  They measured 
equivalent widths for the 2.205\,$\mu$m \ion{Na}{1} doublet and 2.263\,$\mu$m \ion{Ca}{1} triplet, 
along with a pseudo-continuum index defined over three narrow passbands, 2.070--2.090, 
2.235--2.255, and 2.360--2.380\,$\mu$m (see their Fig.~2 for a useful visualization), designed to 
probe the spectral curvature induced by H$_2$O absorption bands.  With reference to a custom grid 
of the {\sc BT-Settl} modifications of the {\sc Phoenix} library \citep{allard12}, 
\citeauthor{rojas-ayala12}~infer $T_{\rm eff} = 3039\pm56$\,K and $[{\rm Fe/H}] = 0.28\pm0.17$ for 
a fixed $\log g = 5.0$.

@@

\section{Spectral Emulator for Interpolation} \label{sec:Appendix}

Interpolation from a library of synthetic spectra is conceptually straightforward, but in the 
application being considered here there are some subtleties that necessitate a more sophisticated 
approach.  Spectral line formation is a non-linear process, where line shapes are determined by 
complex radiative transfer through a stellar atmosphere.  Any interpolation process aims to bypass 
this non-linear process and predict the behavior of many different spectral lines for an arbitrary 
set of parameters based on a pre-computed set of library spectra with similar (neighboring) 
parameters.  In this Appendix, we describe the procedure through which we propagate an empirical 
approximation of the {\it uncertainty} in that prediction -- which can be substantial -- into and 
through the probabilistic inference framework we have developed.
